State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources

### 2021-03-26 analysis/paper/appendices/Appendix_simulation_details.Rmd
started to address reviewer comments
changed the title and tag of simulation appendix since model framework one is being dropped
round of edits from Mike

# Appendix B - Simulation Details {#append2}

To simulate fish passing a dam, an $\mathbb{R}$ software function was developed [@R-Core-Team2020]. The function randomly samples observations from assumed probability distribution functions (pdf) with known parameters. Total unique fish, $N$, and a vector, $\omega$, containing the proportions of wild ($w$), hatchery ($h$) and hatchery no-clip ($hnc$) fish passing the dam is set to establish known "truths" of escapement by origin.

@@

All code for simulating data and fitting STADEM to that data can be found at [https://www.github.com/KevinSee/ManuscriptSTADEM]([https://www.github.com/KevinSee/ManuscriptSTADEM]).

>>>>

---
output:
  pdf_document: default
  html_document: default
---
# Appendix A - Simulation Details {#append1}

To simulate fish passing a dam, we developed an $\mathbb{R}$ software function [@R-Core-Team2020]. The function randomly samples observations from assumed probability distribution functions (pdf) with known parameters. Total unique fish, $N$, and a vector, $\omega$, containing the proportions of wild ($w$), hatchery ($h$) and hatchery no-clip ($hnc$) fish passing the dam is set to establish known "truths" of escapement by origin.

@@

All code for simulating data and fitting STADEM to that data can be found at [https://www.github.com/KevinSee/ManuscriptSTADEM](https://www.github.com/KevinSee/ManuscriptSTADEM).
